\begin{bib}[100]


% \bibitem{参照用名称}
%   著者名： 
%   \newblock 文献名，
%   \newblock 書誌情報，出版年．


\bibitem{sensorama}
\begin{flushleft}
  J. Balaguer, A. Mangili:
  \newblock Virtual Environments. TR of Comp. Graph. Lab.,
  \newblock Swiss Federal Institute of Technology, Lausanne (1993),
\end{flushleft}

\bibitem{verge}
\begin{flushleft}
  The Verge:
  \newblock The Rise and Fall and Rise of Virtual Reality.,
  \newblock The Verge. N.p., n.d. Web. 24 Jan. 2016.
   \newblock {\it http://www.theverge.com/a/virtual-reality/intro}.
\end{flushleft}

\bibitem{touch}
\begin{flushleft}
  OCULUS:
  \newblock Touch by Oculus | Oculus,
  \newblock Oculus N.p., n.d. Web. 24 Jan. 2016.
   \newblock {\it https://www.oculus.com/en-us/touch/}.
\end{flushleft}

\bibitem{vive}
\begin{flushleft}
  VIVE:
  \newblock "THIS IS REAL." HTC VIVE HOME,
  \newblock Vive N.p., n.d. Web. 24 Jan. 2016.
   \newblock {\it https://www.htcvive.com/us/}.
\end{flushleft}

\bibitem{samsung}
\begin{flushleft}
  Samsung Gear VR:
  \newblock The Official Samsung Galaxy Site.,
  \newblock Samsung N.p., n.d. Web. 24 Jan. 2016.
   \newblock {\it http://www.samsung.com/global/galaxy/wearables/gear-vr/}.
\end{flushleft}

\bibitem{cardboard}
\begin{flushleft}
  Google Cardboard:
  \newblock Google Developers Blog,
  \newblock Cardboard N.p., n.d. Web. 24 Jan. 2016.
   \newblock {\it http://googledevelopers.blogspot.jp/2014/12/google-cardboard-seriously-fun.html}.
\end{flushleft}

\bibitem{vrtrendShiny}
\begin{flushleft}
  Shiny Mathew:
  \newblock Importance of Virtual Reality in Current World,
  \newblock International Journal of Computer Science and Mobile Computing A Monthly Journal of Computer Science and Information Technology IJCSMC, Vol. 3, Issue. 3, 3, March 2014, pg.894 \UTF{2013} 899,
\end{flushleft}

\bibitem{vrtrendSamuel}
\begin{flushleft}
  Samuel Ebersole:
  \newblock A Brief History of Virtual Reality and its Social Applications, Academia.edu,
  \newblock Jan 1, 1997,  pg.3.
\end{flushleft}

\bibitem{vrtrendSamuel}
\begin{flushleft}
  Samuel Ebersole:
  \newblock A Brief History of Virtual Reality and its Social Applications, Academia.edu,
  \newblock Jan 1, 1997,  pg.3.
\end{flushleft}

\bibitem{oculus}
\begin{flushleft}
  Shacknews:
  \newblock Oculus VR Co-founder Explains the Challenges of Virtual Reality Gaming,
  \newblock {\it http://www.shacknews.com/article/78616/oculus-vr-co-founder-explains-the-challenges-of-virtual-reality}.
\end{flushleft}

\bibitem{HMDifficulties}
\begin{flushleft}
  Wired:
  \newblock Here’s What We Need to Do to Get VR to Take Off.,
  \newblock Conde Nast Digital, n.d. Web. 24 Jan. 2016
  \newblock {\it http://www.wired.com/2015/08/vr-creative-process/}.
\end{flushleft}

\bibitem{dream}
\begin{flushleft}
『大辞泉 第二版』小学館:
  \newblock 2012 年 11 月 2 日
 \end{flushleft}

\bibitem{saintDenys}
\begin{flushleft}
Hervey de Saint-Denys:
  \newblock Transl.: Dream and the Ways to Direct Them: Practical Observations
  \newblock 1867
  \newblock Paris: Librairie d'Amyot, \UTF{00C9}diteur, 8, Rue de la Paix.
 \end{flushleft}
 
  \bibitem{LaBerge}
\begin{flushleft}
 LaBerge Stephen and Howard Rheingold:
  \newblock Exploring the World of Lucid Dreaming,
  \newblock New York: Ballantine, 1990. Print.
 \end{flushleft}
 
  \bibitem{tsukuba}
\begin{flushleft}
   \newblock "浅い眠りのレム睡眠、記憶定着促す役割　筑波大など発表：朝日新聞デジタル." ,
  \newblock 朝日新聞デジタル. N.p., 25 Oct. 2015.
  \newblock Web. 16 Jan. 2016.
  \newblock{\it http://www.asahi.com/articles/ASHBR316YHBRULBJ004.html}.
\end{flushleft}

  \bibitem{Dement}
\begin{flushleft}
  Dement, W.C:
  \newblock  The promise of sleep,
  \newblock Delacorte Press,
  \newblock 1999,
 \end{flushleft}
 
 \bibitem{freud}
\begin{flushleft}
  Sigmund Freud:
  \newblock The Interpretation of Dreams (1900).,
  \newblock Sigmund Freud: The Interpretation of Dreams</i>. N.p., n.d. 2015.
\end{flushleft}
 
  \bibitem{Zhang}
\begin{flushleft}
 Zhang, Jie:
  \newblock Memory process and the function of sleep,
  \newblock Journal of Theoretics Retrieved March 13, 2006.
 \end{flushleft}
 
 \bibitem{iSleep}
\begin{flushleft}
  Tian Hao, Guoliang Xing, Gang Zhou:
  \newblock  iSleep: Unobtrusive Sleep Quality Monitoring using Smartphones,
  \newblock SenSys’13,
  \newblock  November 11\UTF{2013}15, 2013, Rome, Italy
\end{flushleft}

\bibitem{beddit}
\begin{flushleft}
  beddit.com:
  \newblock Beddit Sleep Monitor and the Science Behind It,
  \newblock Beddit Science Leafle HR, 29 Aug. 2014.
\end{flushleft}
  
\bibitem{takaratomi}
\begin{flushleft}
  タカラトミー:
  \newblock "好きな夢が見られる？　タカラの安眠グッズ「夢見工房」." ,
  \newblock ITmedia LifeStyle. N.p., n.d.
  \newblock Web. 08 Jan. 2016.
  \newblock{\it http://www.itmedia.co.jp/lifestyle/articles/0401/14/news047.html}.
\end{flushleft}

\bibitem{dreamOn}
\begin{flushleft}
  Dream:ON:
  \newblock "Dream:ON - The App to Influence Your Dreams.",
  \newblock The App to Influence Your Dreams. N.p., n.d. Web.
  \newblock Web. 08 Jan. 2016.
  \newblock{\it http://www.dreamonapp.com/}.
\end{flushleft}

\bibitem{yumemiru}
\begin{flushleft}
  Yumemiru:
  \newblock  "見たい夢が見られるかも？｜ユメミ〜ル.",
  \newblock Web. 16 Jan. 2016.
  \newblock{\it http://www.technology-miraiworks.com/yume/}.
\end{flushleft}

\bibitem{DreamDream}
\begin{flushleft}
  Dream:ON:
  \newblock "夢操作アプリ- Dream×Dreamを App Store で.",
  \newblock App Store. N.p., n.d. Web. 16 Jan. 2016.
  \newblock{\it https://itunes.apple.com/jp/app/meng-cao-zuoapuri-dream-dream/id509989267?mt=8}.
\end{flushleft}

\bibitem{remNonRem}
\begin{flushleft}
  Patrick McNamara, Patricia Johnson, Deirdre McLaren, Erica Harris, Catherine Beauharnais, Sanford Auerbach:
  \newblock "International Review of Neurobiology",
  \newblock Volume 92, 2010, Pages 69\UTF{2013}86.
\end{flushleft}

\bibitem{hypnogram}
\begin{flushleft}
  Catalyst Athletics:
  \newblock Understanding Sleep for Optimal Recovery and Productivity.,
  \newblock By Travis Cooper. N.p., n.d. Web. 24 Jan. 2016,
  \newblock{\it http://www.catalystathletics.com/article/1845/Understanding-Sleep-for-Optimal-Recovery-Productivity/}.
\end{flushleft}

\bibitem{negaeri}
\begin{flushleft}
  Kevin Morton:
  \newblock "The Five Stages of Sleep: Characteristics of Non-REM REM.",
  \newblock Stanford Sleep Book, n.d. Web. 15 Jan. 2016.
  \newblock{\it http://www.end-your-sleep-deprivation.com/stages-of-sleep.html}.
\end{flushleft}

\bibitem{reasonToDream}
\begin{flushleft}
  野村総合研究所 金融ITイノベーション研究部:
  \newblock 夢─脳内情報整理の仕組み─,
  \newblock 「金融 IT フォーカス」編集事務局,
  \newblock  2006,
\end{flushleft}

\bibitem{forgetDreams}
\begin{flushleft}
  Dharani, Krishnagopal:
  \newblock The Biology of Thought: A Neuronal Mechanism in the Generation of Thought,
  \newblock a New Molecular Model. N.p.: n.p., n.d. Print.
\end{flushleft}

\bibitem{cortex}
\begin{flushleft}
  Trimble, M. R.:
  \newblock The Prefrontal Cortex: Anatomy, Physiology and Neuropsychology of the Frontal Lobe.,
  \newblock  British Journal Of Psychiatry (1989).
\end{flushleft}

\bibitem{omron}
\begin{flushleft}
  Omron:
  \newblock  "ねむり時間計 HSL-002C｜睡眠計・ねむり時間計｜商品情報 | オムロン ヘルスケア",
  \newblock オムロン ヘルスケア. N.p., n.d. Web. 15 Jan. 2016,
  \newblock{\it http://www.healthcare.omron.co.jp/product/hsl/hsl-002c.html}.
\end{flushleft}

\bibitem{neuroon}
\begin{flushleft}
  Neuroon:
  \newblock  "Neuroon - an Intelligent Sleep Mask."
  \newblock Neuroon. N.p., n.d. Web. 08 Jan. 2016.
  \newblock{\it https://neuroon.com/technology/}.
\end{flushleft}

\bibitem{beWellApp}
\begin{flushleft}
  Zhenyu Chen, Mu Lin, Fanglin Chen, Nicholas D. Lane, Giuseppe Cardone, Rui Wang, Tianxing Li, Yiqiang Chen, Tanzeem Choudhury, Andrew T. Campbell:
  \newblock  Unobtrusive Sleep Monitoring using Smartphones,
  \newblock 2013 7th International Conference on Pervasive Computing Technologies for Healthcare and Workshops, pg. 145~152,
  \newblock 2013.252148
\end{flushleft}

\bibitem{sleepSheep}
\begin{flushleft}
  長塚 麻美, 串山 久美子, 馬場 哲晃:
  \newblock  The Interface to Improve the Quality of Sleep by the Sleep Depth Determination Using the Motion Detection,
  \newblock 情報処理学会 インタラクション 2015 IPSJ Interaction 2015,
  \newblock  A16 2015/3/5,
\end{flushleft}

\bibitem{iWinks}
\begin{flushleft}
iWinks:
 \newblock  "The Ultimate Lucid Dreaming Tool." ,
  \newblock N.p., n.d. Web. 08 Jan. 2016,
  \newblock{\it https://iwinks.org/}.
\end{flushleft}

\bibitem{roseDream}
\begin{flushleft}
Carroll:
 \newblock  "Smells Influence Dreams" ,
  \newblock National Geographic. National Geographic Society, n.d. Web. 17 Jan. 2016,
  \newblock{\it http://news.nationalgeographic.com/news/2008/09/080923-smell-sleep.html}.
\end{flushleft}

\bibitem{pavlov}
\begin{flushleft}
Todes, Daniel Philip:
 \newblock  "Pavlov's Physiology Factory" ,
  \newblock Baltimore MD: Johns Hopkins University Press. pp. 232,
\end{flushleft}

\end{bib}